\documentclass{article}

\usepackage[main]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[textsize=tiny, textwidth=2.6cm]{todonotes}
\setlength{\marginparwidth}{2.6cm}
\usepackage{listings}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\DeclareMathOperator{\tr}{tr}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\OG}{\mathrm{O}}

\newcommand{\reviewquestion}[1]{\todo[inline,color=blue!8]{Nina: #1}}
\newcommand{\papertodo}[1]{\todo[inline,color=orange!12]{TODO: #1}}
\newcommand{\decision}[1]{\todo[inline,color=green!10]{Decision needed: #1}}

\lstset{
  language=Python,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{red},
  frame=single,
  breaklines=true,
  columns=fullflexible,
}

\title{\texttt{bispectrum}: Selective $G$-Bispectra Made Practical}

\author{%
  Johan Mathe \\
  Atmo, Inc. \\
  \texttt{johan@atmo.ai} \\
  \And
  Nina Miolane \\
  University of California, Santa Barbara \\
  \texttt{nmiolane@ucsb.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
\papertodo{Write a clean 120--150 word abstract after we decide the final empirical scope.}
\reviewquestion{Should the paper pitch itself primarily as a software paper with one engineering/scientific case study, or as a software paper plus empirical ML paper?}
\reviewquestion{For the abstract, should we keep the empirical claim to PCam only unless a second experiment is complete enough to defend?}

Candidate abstract structure:
\begin{itemize}
  \item Problem: selective $G$-bispectra are theoretically attractive but not available as practical ML software.
  \item Main artifact: a PyTorch library implementing selective or full bispectral invariants across several group/domain pairs.
  \item Main technical point: implementing inversion for the octahedral group required resolving a concrete algorithmic failure of the bootstrap strategy.
  \item Empirical point: evaluate the library as an invariant pooling primitive on PatchCamelyon, with final claims deferred until sweeps are complete.
  \item Scope note: do not mention steerable-to-Fourier in this version.
\end{itemize}
\end{abstract}

\reviewquestion{We need a 3D dataset to test the Octahedral group (\texttt{OctaonOcta}). This is required for the empirical story to cover our main technical contribution.}
\reviewquestion{Deadline is April 14 for internal review.}
\reviewquestion{We need to look again at the state of the art for the PCam dataset --- make sure our baselines and comparisons are up to date.}
\reviewquestion{We need to do a Pareto analysis for the amount of data (accuracy vs.\ training set size across pooling methods).}

\section{Introduction}
\label{sec:intro}

Equivariant neural networks enforce symmetry by construction, but they still
require an invariant representation at the point where a prediction must no
longer depend on orientation. In practice, invariant pooling remains a weak
point: standard choices such as norm pooling, gate-based pooling, or max/sum
aggregation are usable, but they do not preserve all equivariant information.
The bispectrum offers a mathematically principled alternative, since for many
groups it yields exact invariants with reconstruction guarantees.

The obstacle is practical rather than conceptual. Existing bispectral
constructions are scattered across theory papers, domain-specific derivations,
and small implementations, with no general-purpose PyTorch library covering the
finite-group and compact-group cases relevant to modern geometric deep learning.
Even for groups where selectivity reduces the coefficient count from
$O(|G|^2)$ to $O(|G|)$, a user still needs a numerically stable implementation,
a consistent API, inversion routines, tests, and benchmarked runtime behavior.

This paper presents \texttt{bispectrum}, a PyTorch library for computing
bispectral invariants and, where available, their inverses. The library
supports cyclic, dihedral, torus, disk, sphere, and octahedral settings as
differentiable \texttt{nn.Module}s intended to plug into standard ML workflows.
Our emphasis in this draft is on the software design and on one specific
engineering contribution that arose during implementation: inversion for the
octahedral group.

\papertodo{Rewrite the introduction once the final empirical scope is fixed.}
\decision{Keep the paper centered on the library + octahedral inversion, or broaden to ``library + empirical study of invariant pooling''?}
\reviewquestion{Do we want the intro to frame the library as infrastructure for geometric deep learning in general, or specifically as a practical invariant nonlinearity for equivariant CNNs?}

\paragraph{Proposed contributions for this version.}
This scaffold assumes the paper will make the following contributions:
\begin{enumerate}
  \item \textbf{Software contribution.} A PyTorch library implementing
    bispectral invariants for multiple group/domain pairs with a consistent
    \texttt{nn.Module}-style interface.
  \item \textbf{Engineering/scientific contribution.} An analysis of why the
    standard selective-bispectrum bootstrap inversion fails for the octahedral
    group, together with a working bootstrap + Levenberg--Marquardt correction.
  \item \textbf{Empirical contribution.} A task-driven evaluation of the
    library as an invariant pooling primitive, with final claims currently left
    open pending completed sweeps.
\end{enumerate}

\reviewquestion{Is this the right level of ambition for a one-month deadline, or should we cut to only (1) + (2) with experiments framed as validation rather than broad empirical claims?}

\section{Mathematical Background}
\label{sec:background}

\subsection{Equivariant features and invariant maps}

\papertodo{Write a short background subsection on equivariant CNNs and invariant pooling. Keep this focused and non-controversial.}

Suggested points:
\begin{itemize}
  \item Equivariant layers transform predictably under a group action.
  \item Downstream prediction tasks often require a representation invariant to
    that action.
  \item Existing invariant maps in equivariant architectures are typically
    chosen for convenience rather than completeness.
  \item The paper only needs enough background to motivate the bispectrum as a
    candidate invariant primitive.
\end{itemize}

\subsection{The $G$-bispectrum and selective bispectra}

\papertodo{Write a concise subsection giving the bispectrum definition and the idea of selectivity.}

Minimal content to include:
\begin{itemize}
  \item finite-group Fourier transform notation,
  \item the bispectrum as a triple-product / Clebsch--Gordan construction,
  \item completeness as orbit separation under appropriate nondegeneracy assumptions,
  \item selective bispectrum as a reduced coefficient set with the same recovery guarantees in the settings covered by prior theory.
\end{itemize}

\reviewquestion{Should this section stay abstract and general, or should we immediately specialize notation toward the modules in the library table?}

\section{The \texttt{bispectrum} Library}
\label{sec:library}

This section should read like a software paper, not a tutorial. The goal is to
explain what the library covers, what abstractions it exposes, and what design
choices were made to keep the implementation mathematically legible and usable
in PyTorch workflows.

\subsection{Design principles}
\label{sec:design}

\papertodo{Write this as a design-principles section, borrowing the ``manifesto'' framing from strong software papers.}

Candidate principles:
\begin{itemize}
  \item \textbf{Mathematical naming.} Module names encode both the acting group
    and the signal domain, e.g.\ \texttt{CnonCn}, \texttt{DnonDn},
    \texttt{SO2onDisk}, \texttt{SO3onS2}, \texttt{OctaonOcta}.
  \item \textbf{\texttt{nn.Module} interface.} Every transform is packaged as a
    module with a forward pass and, where available, an inversion routine.
  \item \textbf{Raw-signal input.} Users pass signals in their natural domain;
    the internal Fourier or harmonic transform is handled by the module.
  \item \textbf{Registered buffers for mathematical objects.} Precomputed
    Clebsch--Gordan matrices, harmonic bases, and related constants move
    correctly across device and dtype.
  \item \textbf{Selective when justified.} Modules expose selective outputs when
    the mathematics and implementation support them; otherwise the paper should
    state the limitation explicitly.
\end{itemize}

\reviewquestion{Do we want to include a short subsection here on what the library deliberately does \emph{not} try to unify, to avoid overclaiming API uniformity?}

\subsection{Supported modules}
\label{sec:supported-modules}

\papertodo{Fill in the table only with claims that the current package actually supports. Avoid wording that implies full-mode support everywhere.}

\begin{table}[h]
  \caption{Current scope of the \texttt{bispectrum} library.}
  \label{tab:supported-groups-scaffold}
  \centering
  \small
  \begin{tabular}{llll}
    \toprule
    Module & Group / Domain & Output mode & Inversion status \\
    \midrule
    \texttt{CnonCn} & $C_n$ on $C_n$ & selective + full & implemented \\
    \texttt{SO2onS1} & $\SO(2)$ on $S^1$ & selective + full via cyclic case & implemented \\
    \texttt{TorusOnTorus} & product cyclic groups on torus & selective + full & implemented \\
    \texttt{DnonDn} & $D_n$ on $D_n$ & selective & implemented \\
    \texttt{SO2onDisk} & $\SO(2)$ on disk & selective & implemented \\
    \texttt{SO3onS2} & $\SO(3)$ on $S^2$ & full only & not implemented \\
    \texttt{OctaonOcta} & octahedral group & selective & implemented \\
    \bottomrule
  \end{tabular}
\end{table}

\papertodo{Verify exact wording for the octahedral domain and whether we want to call it ``on $\R^3$'', ``on the octahedral group'', or something more implementation-specific.}

\subsection{Example API}
\label{sec:api}

\papertodo{Include one short code snippet that actually matches the public package API.}

\begin{lstlisting}
import torch
from bispectrum import CnonCn, SO2onDisk, OctaonOcta

bsp = CnonCn(n=8, selective=True)
f = torch.randn(16, 8)
beta = bsp(f)
f_rec = bsp.invert(beta)
\end{lstlisting}

\reviewquestion{Should the paper include a single minimal code example only, or one example per modality (finite group, disk, sphere)?}

\subsection{Octahedral inversion as an implementation case study}
\label{sec:octa}

The clearest technical case study in the library is inversion for the
octahedral group. Implementing \texttt{OctaonOcta} exposed a failure mode of
the standard bootstrap strategy: the selective bispectrum remains complete, but
the sequential reconstruction procedure breaks because the ambiguity recovered
at the first nontrivial irrep lives in $\SO(3)$, while the octahedral
Clebsch--Gordan structure only block-diagonalizes the discrete group action.

\papertodo{Write this section as a focused engineering/scientific contribution, not as a broad new theory section.}

Core points to cover:
\begin{itemize}
  \item what the bootstrap strategy tries to do,
  \item why it works in cyclic and dihedral settings,
  \item what fails in the octahedral case,
  \item how the library resolves this in practice using bootstrap
    initialization plus Levenberg--Marquardt refinement and multiple restarts.
\end{itemize}

\reviewquestion{Should this be the central scientific contribution in the paper, with the rest of the library framed as the enabling software context?}

\section{Benchmarks}
\label{sec:benchmarks}

\papertodo{Add benchmark figures only after the benchmark script and naming are cleaned up.}
\papertodo{Decide whether to present both coefficient-count scaling and wall-clock timing, or to prioritize coefficient-count scaling plus one throughput plot.}
\reviewquestion{Do we want to report only the benchmark regimes that are already stable and reproducible, or keep broader benchmark ambitions in appendix as future work?}

Candidate benchmark questions for co-author review:
\begin{itemize}
  \item Which benchmark best supports the software-paper narrative: coefficient
    scaling, forward runtime, inversion runtime, memory, or all of the above?
  \item Should runtime figures compare only supported modes, to avoid paper/code mismatch?
  \item Do we need two GPU types for credibility, or is one clean benchmarked setup enough for submission?
\end{itemize}

\section{Experiments}
\label{sec:experiments}

This section is intentionally scaffolded as a planning document rather than a
final claim section. The main purpose is to give co-authors something concrete
to react to while experimental sweeps are still being completed.

\subsection{Primary empirical story: PatchCamelyon}
\label{sec:pcam}

\papertodo{Write the final setup subsection only after deciding which models and seeds are complete enough to defend.}

Proposed stable framing:
\begin{itemize}
  \item Dataset: PatchCamelyon, since rotation invariance is physically
    meaningful in histopathology.
  \item Architecture: equivariant DenseNet with a fixed backbone template.
  \item Experimental variable: invariant pooling/nonlinearity choice.
  \item Goal: evaluate whether a bispectral invariant is competitive as a
    practical pooling primitive.
\end{itemize}

\decision{Main comparison set for the final paper: standard vs norm vs gate vs Fourier-ELU vs bispectrum, or a narrower comparison if some baselines remain incomplete?}
\decision{Will the final main table use only fully matched seeds and train fractions, even if that means dropping some partially completed runs?}
\reviewquestion{Given the current results, should the main empirical claim be modest (``competitive and exact'') rather than aggressive (``outperforms baselines'') unless additional sweeps close the gap?}

\subsection{Data-efficiency and robustness}
\label{sec:robustness}

\papertodo{Only keep this subsection in the main paper if the 1\% / low-data results are complete enough to be interpretable.}

Questions for review:
\begin{itemize}
  \item Is low-data performance central enough to merit a main-paper figure?
  \item If the low-data story is mixed, should the figure emphasize rotation
    stability rather than data efficiency?
  \item Is it better to present low-data results as exploratory evidence rather
    than as a headline claim?
\end{itemize}

\subsection{Optional second experiment}
\label{sec:second-exp}

\papertodo{Decide whether to keep a placeholder for a second task at all.}
\reviewquestion{Do we want a second experiment in the submission if it is not clearly stronger than the PCam story?}
\reviewquestion{Is it better to submit a tighter single-task paper than a broader paper with an underdeveloped second empirical section?}

If a second task remains incomplete near the deadline, this scaffold assumes it
should be cut rather than weakly included.

\section{Related Work}
\label{sec:related}

\papertodo{Write this section around software/tools and practical distinctions, not around the abandoned steerable-to-Fourier narrative.}

Suggested structure:
\begin{itemize}
  \item equivariant deep learning libraries such as \texttt{e2cnn}/\texttt{escnn},
  \item classical and modern bispectrum theory,
  \item selective bispectrum papers for finite groups and the disk,
  \item bispectral CNNs in the Depeursinge/Oreiller line,
  \item tensor-product and Clebsch--Gordan nonlinearities,
  \item software-paper precedents at NeurIPS.
\end{itemize}

\reviewquestion{How aggressively should we distinguish this paper from prior bispectral CNN work?}
\reviewquestion{Should we explicitly say that our contribution is breadth of group/domain support + inversion + PyTorch integration, rather than claiming the general idea of bispectral invariants in CNNs is new?}

\section{Discussion and Limitations}
\label{sec:discussion}

\papertodo{Write this section early, not last. It can help constrain the rest of the paper.}

Minimum limitations to acknowledge:
\begin{itemize}
  \item selective $\SO(3)$ on $S^2$ remains open,
  \item inversion is not available for every supported transform,
  \item empirical evaluation is currently narrower than the full intended
    application scope of the library,
  \item some benchmark or experimental claims may need to be trimmed to match
    the completed evidence.
\end{itemize}

\reviewquestion{Should the limitations section explicitly state that the paper does not attempt a general theory of bispectral pooling for arbitrary steerable representations?}

\paragraph{Roadmap.}
\papertodo{Add a brief roadmap paragraph for PI/co-author review.}

Candidate roadmap items:
\begin{itemize}
  \item finish stable benchmark scripts and plots,
  \item finish matched PCam sweeps,
  \item improve docs/examples for public release,
  \item future work on selective $\SO(3)$ and richer empirical applications.
\end{itemize}

\section{Conclusion}
\label{sec:conclusion}

\papertodo{Write a short conclusion once the final scope is fixed.}

Proposed conclusion shape:
\begin{itemize}
  \item restate the library contribution,
  \item emphasize octahedral inversion as the main technical case study,
  \item summarize what the completed experiments support,
  \item end with realistic next steps rather than broad claims.
\end{itemize}

\begin{ack}
\papertodo{Add acknowledgments for camera-ready.}
\end{ack}

\bibliographystyle{plainnat}
\bibliography{references}

\appendix

\section{Implementation Details}
\label{app:impl}

\papertodo{Collect package-level implementation details that do not fit in the main paper: buffers, transforms, inversion APIs, optional dependencies, dtype/device behavior.}

\section{Benchmark Details}
\label{app:bench}

\papertodo{Include full benchmark tables only after the benchmark script is cleaned up and the figures are final.}

\section{Experimental Details}
\label{app:exp}

\papertodo{Include architecture details, hyperparameters, seeds, train fractions, hardware, and exact result aggregation procedures.}
\reviewquestion{Do we want appendix-level tables for every completed sweep, or only the ones directly supporting the paper's final claims?}

\newpage
\input{checklist.tex}

\end{document}
